The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-16 document/ms.tex
adding exosyspop footnote

\widowpenalty=100000
\clubpenalty=100000

@@

The candidate in the light curve of KIC~4754460 as an individual transit
candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
at the beginning of Quarter 17.
This eclipse was missed by the automated search because only the second half
of the eclipse is observed.
The most likely explanation of this system is that the listed candidate is the
secondary eclipse of a binary system but we will keep the candidate is the
list and treat this effect statistically in \sect{false-positives}.

@@

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the python
package \exosyspop\ \citep{Morton:2016b}, which we developed for this
purpose.

>>>>

\widowpenalty=10000
\clubpenalty=10000

@@

Five candidate transit events in the light curves of four targets were
rejected because of a significant centroid shift or a large impact parameter.
These events are probably astrophysical eclipses from binary star systems that
were not found by previous studies of long-period eclipsing binary systems.
We do not consider these events further in the rest of this \paper\ but
Table~\ref{tab:rejects} lists these events and their properties for
posterity.

The candidate in the light curve of KIC~4754460 is an individual transit
candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
at the beginning of Quarter 17.
This eclipse was missed by the automated search because only the second half
of the eclipse is observed.
The most likely explanation of this system is that the listed candidate is the
secondary eclipse of a binary system but we will keep the candidate is the
list and treat this effect statistically in \sect{false-positives}.

@@

\begin{floattable}
\begin{deluxetable}{ccccl}
\tabletypesize{\footnotesize}
\caption{The signals rejected with a centroid shift or large impact parameter
\label{tab:rejects}}
\include{rejecttab}
\end{deluxetable}
\end{floattable}

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}}, which
we developed for this purpose.
